\documentclass[10pt,letterpaper]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES AND THEMES
%----------------------------------------------------------------------------------------
\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontawesome5}

% Define links style
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=teal,
}

% Custom section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

%----------------------------------------------------------------------------------------
%	CUSTOM COMMANDS
%----------------------------------------------------------------------------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

%----------HEADING-----------------
\begin{center}
    {\Huge \scshape Sambit Mishra} \\ \vspace{2pt}
    \small PhD Student, Electrical \& Computer Engineering $|$ University of Southern California \\ \vspace{2pt}
    \href{mailto:sambitmi@usc.edu}{\faEnvelope \ sambitmi@usc.edu} $|$ \href{https://sambitmishra.in}{\faGlobe \ sambitmishra.in}
\end{center}

%-----------RESEARCH FOCUS-----------------
\section{Research Focus}
\small{
Causal inference and probabilistic graphical models, with emphasis on identifiability theory, design of efficient discovery algorithms for identifiable causal DAGs, and analysis on bounds and design of lowest variance discovery algorithms for non-identifiable or partially-identifiable cases, with focus on scalable continuous optimization methods for causal discovery in high-dimensional data, and mixed distribution-based datasets.
}
\vspace{-8pt}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Southern California (USC)}{Los Angeles, CA, USA}
      {Ph.D. in Electrical and Computer Engineering; Advisor: Prof. Urbashi Mitra}{Aug 2025 -- Present}
      \resumeItem{\textbf{GPA: 4.00/4.00}}
      \resumeItem{\textbf{Key Coursework:} Probability Theory (EE 503 - Fall 2025, Grade: A), Linear Algebra (EE 510 - Fall 2025, Grade: A), Supervised Machine Learning (EE 559 - Spring 2026, Grade: A), Inference \& Estimation Theory (EE 563 - Spring 2026, Grade: A).}

    \vspace{10pt}

    \resumeSubheading
      {Indian Institute of Technology (IIT) Bhubaneswar}{Bhubaneswar, Odisha, India}
      {B.Tech. (Hons.) in Electronics and Communication Engineering; Advisor: Dr. Soumya P. Dash}{2021 -- 2025}
      \resumeItem{\textbf{GPA: 9.14/10.00}}
  \resumeSubHeadingListEnd

%-----------RESEARCH EXPERIENCE-----------------
\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
  {Graduate Research Assistant}{Los Angeles, CA, USA}
  {Ming Hsieh Department of Electrical and Computer Engineering, USC}{Aug 2025 -- Present}
  \begin{itemize}[leftmargin=*, noitemsep]
    \resumeItem{Developing continuous optimization methods for scalable DAG estimation using differentiable constraints to reduce iterations and enable large-scale batching.}
    \resumeItem{Designed a soft-intervention selection framework to improve causal discovery efficiency and lower experimental costs.}
    \resumeItem{Studying identifiability of causal graphs under finite samples and latent variable settings.}
    \resumeItem{Built GPU-accelerated structure learning pipelines in PyTorch using Adam and L-BFGS for non-convex optimization.}
  \end{itemize}

    \resumeSubheading
      {Undergraduate Researcher}{Bhubaneswar, Odisha, India}
      {School of Electrical and Computer Sciences, IIT Bhubaneswar}{Aug 2024 -- May 2025}
      \begin{itemize}[leftmargin=*, noitemsep]
        \resumeItem{Developed SER-optimized modulation schemes for RIS-assisted non-coherent communication systems.}
        \resumeItem{Conducted error analysis for multi-level ASK modulations, optimizing energy efficiency.}
      \end{itemize}

  \resumeSubHeadingListEnd

%-----------PUBLICATIONS (HIGHLIGHTED)-----------------
\section{Publications}
\small \begin{enumerate}[leftmargin=*, label={[\arabic*]}]
    \item  C. Peng, \textbf{S. Mishra}, U. Mitra, ``Learning to Intervene: Optimized Soft Intervention Selection for Causal Discovery,'' \textit{IEEE Int. Conf. on Acoustics, Speech and Signal Processing (ICASSP)}, accepted, 2026.

    \item \textbf{S. Mishra}, S. P. Dash and G. C. Alexandropoulos,``SER-Optimized Multi-Level ASK Modulations for RIS-Assisted Communications With Energy- and Sign-Based Noncoherent Reception," in \emph{IEEE Transactions on Green Communications and Networking}, vol. 10, pp. 1433-1445, 2026, doi: 10.1109/TGCN.2025.3633182.

    \item \textbf{S. Mishra} and S. P. Dash,``Error Analysis With Optimal Receiver and Multi-Level ASK for RIS-Assisted Noncoherent Wireless System," in \emph{IEEE Wireless Communications Letters}, vol. 15, pp. 300-304, 2026, doi: 10.1109/LWC.2025.3624154.

\end{enumerate}

\section{Awards \& Academic Distinctions}
\begin{itemize}[leftmargin=*, noitemsep]
  \item Secured All India Rank 4000 among $\sim$1{,}000{,}000 candidates in JEE Advanced 2021, India
  \item Awarded National Talent Search Scholarship by achieving a rank among the top 2000 students among $\sim$1{,}200{,}000 candidates in National Talent Search Examination (NTSE) 2019, Government of India
  \item Qualified Regional Mathematical Olympiad (RMO) 2019; Selected participant, Indian National Mathematical Olympiad (INMO) 2020
\end{itemize}

\section{Technical Skills}
 \begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Causal Inference:} Causal Discovery, Bayesian Networks, Structural Equation Models
    \item \textbf{Optimization:} Gradient-based solvers (Adam, RMSProp, L-BFGS), Convex Optimization, Bilevel Optimization.
    \item \textbf{Programming \& Tools:} Python (PyTorch, NumPy, SciPy), C++, CUDA, MATLAB, Git, LaTeX.
 \end{itemize}

%-----------INDUSTRY EXPERIENCE (COMPRESSED)-----------------
\section{Industry Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {NVIDIA Corporation}{Bengaluru, Karnataka, India}
      {ASIC Engineering Intern, CHI VIP Team}{May 2024 -- July 2024}
      \vspace{8pt}
      \newline
      Verified CHI protocol compliance for CPU/GPU IPs using SystemVerilog and Perl automation; ensured interoperability between internal and external verification IPs.
  \resumeSubHeadingListEnd

\end{document}
